---
title: "Plot method demonstration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot method demonstration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(osmose)
```

```{r, include = FALSE}
# Remove the .jar file if exits.
osmose:::flushCache("osmose_4.3.0.jar")
osmose:::flushCache("eec_4.3.0")
```

### Create, run and read an example

Define a folder for copy example files:
```{r, cache=TRUE}
exampleFolder <- tempdir()

# Show the temporary folder
cat(exampleFolder)

# Copy files
demoPaths <- osmose_demo(path = exampleFolder, config = "eec_4.3.0")
```

Run the example using `run_osmose` function (it will take less than 1 min):
```{r}
run_osmose(input = demoPaths$config_file, force=TRUE)
```

Read outputs and config using `read_osmose` function
```{r}
outputs <- read_osmose(path = demoPaths$output_dir, 
                       input = demoPaths$config_file)

# Print osmose outputs
print(outputs)
```

### Plot methods for `osmose` class

```{r, fig.width=5.7, fig.height=4.75, warning=FALSE}
plot(outputs, what = "biomass")
plot(outputs, what = "biomass", type = 2)
plot(outputs, what = "abundance", ts = FALSE, type = 1)
plot(outputs, what = "abundance", ts = FALSE, type = 2)

plot(outputs, what = "biomassByAge")
plot(outputs, what = "biomassBySize", type = 2)
plot(outputs, what = "biomassByTL", type = 1)
plot(outputs, what = "biomassBySize", type = 2)
```

### Plot methods for `osmose.config` class
It is important to remember that config info has already been read in `outputs` object and you can access just by indexing `outputs$config`.

```{r, fig.width=5.7, fig.height=4.75}
plot(outputs$config, what = "species")
plot(outputs$config, what = "predation")
plot(outputs$config, what = "reproduction", type = 1)
plot(outputs$config, what = "reproduction", type = 2)
```
