---
title: "Vignette for osmose package"
author: "Yunne-Jai Shin, Travers Morgane, Verley Philippe, Ricardo Oliveros-Ramos & Laure Velez (2020)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{osmose}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
---

```{r, echo = FALSE, message = FALSE}
library(osmose)
```

# osmose

*Object Oriented Simulator of Marine Ecosystems*

The multispecies and individual-based model (IBM) 'OSMOSE' [@shin2001exploring; @shin2004using] focuses on fish species. This model assumes opportunistic predation based on spatial co-occurrence and size adequacy between a predator and its prey (size-based opportunistic predation). It represents fish individuals grouped into schools, which are characterized by their size, weight, age, taxonomy and geographical location (2D model), and which undergo major processes of fish life cycle (growth, explicit predation, natural and starvation mortalities, reproduction and migration) and fishing exploitation. The model needs basic biological parameters that are often available for a wide range of species, and which can be found in 'FishBase' for instance (see <http://www.fishbase.org/search.php>), and fish spatial distribution data. This package provides tools to build and run simulations using the 'OSMOSE' model.


## Installation

For installing `osmose`, as follows:

```{r, eval=FALSE}
# From CRAN
install.packages("osmose")

# From Github
devtools::install_github("osmose-model/osmose")
```

## About OSMOSE
OSMOSE is a multispecies and Individual-based model (IBM) which focuses on fish species. This model assumes opportunistic predation based on spatial co-occurrence and size adequacy between a predator and its prey (size-based opportunistic predation). It represents fish individuals grouped into schools, which are characterized by their size, weight, age, taxonomy and geographical location (2D model), and which undergo major processes of fish life cycle (growth, explicit predation, natural and starvation mortalities, reproduction and migration) and a fishing mortality distinct for each species [@shin2001exploring; @shin2004using]. OSMOSE, uncoupled version, has been first applied to the Benguela upwelling ecosystem for which 12 fish species have been specified, from small pelagic fish to large demersal species [@shin2004using; @travers2006simulating]. The model needs basic parameters that are often available for a wide range of species, and which can be found in FishBase for instance.


## Main functions

`osmose` package performs three main functions (`read_osmose`, `run_osmose` and `get_var`) and several methods for the outputs (`plot`, `print`, `summary` and `report`). 

### Create example files
`osmose` includes a function that allows to create basic example files in a selected folder. The files corresponds to a case study provided by @Halouani2016. `osmose_demo` uses two main arguments: (1) `path` will be the folder path where the files will be copied and (2) `config` which indicates the configuration example to be copied. To indicate @Halouani2016 case study, `config = "gog"`.
```{r, cache=TRUE}
# Define a folder to copy files
exampleFolder <- tempdir()

cat(exampleFolder)
```

```{r, cache=TRUE}
# Copy files
demoPaths <- osmose_demo(path = exampleFolder, config = "gog")
```

```{r, echo=FALSE}
# Show copied files
cat("Copied files:\n")
print(list.files(path = dirname(demoPaths$config_file), recursive = TRUE))
```

## References