---
title: "Osmose report - Test version of the report"
author: "Osmose package"
date: "`r format(Sys.time(), '%d %B, %Y')`"
fontsize: 10pt
geometry: margin=1cm
keep_tex: yes
output: pdf_document
---

\pagenumbering{gobble}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Automathic report for osmose output class.

## Time series of biomass: for all species with replicates

### plot(gog, what="biomass", ts = TRUE, type=1, col = "gray40")

```{r, echo=FALSE, message=FALSE, fig.height=7, fig.width=8}
plot(gog, what="biomass", ts = TRUE, type=1, col = "gray40")
```

\pagebreak

## Time series of biomass: for four species without replicates

### plot(gog, what="biomass", ts = TRUE, type=1, col = "blue", species = c(0,1,2,3) , replicates = FALSE)

```{r, echo=FALSE, message=FALSE, fig.height=8, fig.width=8}
plot(gog, what="biomass", ts = TRUE, type=1, col = "blue", species = c(0,1,2,3) , replicates = FALSE, initialYear = 1992)
```

## Time series of biomass: type = 2

### plot(gog, what="biomass", type=2, species = c(0,1,2,4,5,6), initialYear = 2000) 
```{r, echo=FALSE, message=FALSE, fig.height=8, fig.width=8}
plot(gog, what="biomass", type=2, species = c(0,1,2,4,5,6), initialYear = 2000)
```

\pagebreak

## Time series of biomass: type = 3

### plot(gog, what="biomass", type=3, start = 25, initialYear = 2002)

```{r, echo=FALSE, message=FALSE, fig.height=8, fig.width=8}
plot(gog, what="biomass", type=3, start = 25, initialYear = 2002) 

```

\pagebreak

## Total biomass: type = 1

### plot(gog, what="biomass", ts = FALSE, type=1, factor = 1e-6)

```{r, echo=FALSE, message=FALSE, fig.height=4.5, fig.width=8}
plot(gog, what="biomass", ts = FALSE, type=1, factor = 1e-6, ci = TRUE)

```

### plot(gog, what="biomass", ts = FALSE, type=1, horizontal=TRUE, ci = FALSE, , cex.names = 0.6) 

```{r, echo=FALSE, message=FALSE, fig.height=4, fig.width=8}
plot(gog, what="biomass", ts = FALSE, type=1, horizontal=TRUE, ci = FALSE, cex.names = 0.6) 
```

\pagebreak

## Total biomass: type = 2 - means over replicates

### plot(gog, what="biomass", ts = FALSE, type=2, col = "green")

```{r, echo=FALSE, message=FALSE, fig.height=4, fig.width=8.5}
plot(gog, what="biomass", ts = FALSE, type=2, col = "green")
```

## Total biomass: type = 3 - means over the time

### plot(gog, what="biomass", ts = FALSE, type=1, horizontal=TRUE, ci = FALSE, , cex.names = 0.6) 

```{r, echo=FALSE, message=FALSE, fig.height=4, fig.width=8.5}
plot(gog, what="biomass", ts = FALSE, type=3, col = "blue")
```

