# Running Osmose

Now that the R package is installed, let's try to run the Osmose demo configuration.

First, launch an `R` console and load the Osmose library:

```{r}
library(osmose)
ls("package:osmose")
```

Now, call the `osmose_demo` function, which allows to copy the reference configuration into your working
directory:

```{r}
demo = osmose_demo(path = "original-demo", config="eec_4.3.0")
demo
```

If some parameters provided in the default configuration must be overwritten, an `extra_args` argument can be provided. It must have the following format:

```{r}
extra_args = "-Psimulation.time.nyear=15 -Poutput.recordfrequency.ndt=1"
```

Here, the `simulation.time.nyear` and `output.recordfrequency.ndt` have been modified. The updated folder can be corrected as follows:

```{r}
demo2 = osmose_demo(path = "modified-demo", config="eec_4.3.0", extra_args=extra_args)
demo2
```



The `demo` object contains the location of the configuration file and extra arguments.

Now, you can run the Osmose model as follows:

```{r}
run_osmose(demo$config_file, parameters=demo$extra_args, force=TRUE)
```

The first argument is the Osmose configuration file, the `parameters` argument allows to overrr

<!--
To run the test configuration, launch `R` and type the following:


```{literalinclude} _static/run_testconf.R
:language: R
```

You should obtain the following figure:

:::{figure} _static/osmose_ref_conf.png
:align: center
:width: 600 px

Outputs of the reference configuration
::: -->
